Reply to Editor

### 2022-03-30 Writing/CEA_3rd_round/replies_rev.rmd
small code changes (clean the codes later)

Please note that this is a stark contrast to "yield" (not EOIR) prediction because yields ARE observable and models can be verified. However, that is not the case for EOIR. This is why you need MC simulations where the data generating process (how yield responds to N, and how field characteristics affect yield response to N) is "known" to the researcher. This way, we can test model's ability to predict EONR, not yield. Any journal article that proposes a new statistical method always accompany the theory of why their method works (consistency of their estimation, etc) with MC simulations where the researchers determines how data is generated and apply their method. This is because we can never test the statistical property of a statistical method in principle using the real data. For example, please see @Wager2018a and @oprescu2019orthogonal

@@

Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that the previous studies relevant to our study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR. There is no study that tests the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (e.g., @Qin2018; @Ransom2019 @Wang2021; @wen2021machine). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We consider those studies not very relevant. We believe including those studies will simply bloat the introduction.

@@

<span style="color:blue">  
We already discuss our results to the state of the art of the literature. The state of the art is sadly trying to predict yields site-specifically as well as possible. We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well). There is nothing wrong with our approach in yield prediction as evident in Figure E.1<!-- Figure 12 -->. We are using ML methods that have been used in the literature of OFE for site-specific input management. Those studies were published very recently. We added our description about how the size of epsilon affects our results briefly in Appendix G. We added the following at line xx page yy:

>>>>

Please note that this is a stark contrast to "yield" (not EOIR) prediction because yields ARE observable and models can be verified. However, that is not the case for EOIR. This is why you need MC simulations where the data generating process (how yield responds to N, and how field characteristics affect yield response to N) is "known" to the researcher. This way, we can test model's ability to predict EONR, not yield. Any journal article that proposes a new statistical method always accompany the theory of why their method works (consistency of their estimation, etc) with MC simulations where the researchers determines how data is generated and apply their method. This is because we can never test the statistical property of a statistical method in principle using the real data. For example, please see @Wager2018a and @oprescu2019orthogonal.

@@

Please see page 3, line 35 for a new list of studies that attempt to estimate EONR. Please note that the previous studies relevant to our study are those that apply ML methods to OFE data with the ultimate intention of estimating site-specific EONR. There is no study that tests the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (e.g., @Qin2018; @Ransom2019 @Wang2021; @wen2021machine). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We consider those studies not very relevant. We believe including those studies will simply bloat the introduction.

@@

<span style="color:blue">  
We already discuss our results to the state of the art of the literature. The state of the art is sadly trying to predict yields site-specifically as well as possible. We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well). There is nothing wrong with our approach in yield prediction as evident in Figure E.1<!-- Figure 12 -->. We are using ML methods that have been used in the literature of OFE for site-specific input management. Those studies were published very recently. We added our description about how the size of epsilon affects our results briefly in Appendix G. We added the following at line 25 page 390:
